%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Professional Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Regional Chair} % Job title
    {Bat1K} % Organization
    {} % Location
    {Jun. 2023 -- Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {I bridge connections between one of the most important worldwide bat consortia and institutions in Ecuador \\ to make them part of cutting-edge genome research.}
        \item {These efforts are expanding the consortium's reach to local students and professionals.}
    \end{cvitems}}
%---------------------------------------------------------
\cventry
{Scientific Consultant} % Job title
{Quiport Corporation} % Organization
{Quito, Ecuador} % Location
{Dec. 2023} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {I analyzed GPS data of two Andean foxes captured in the vicinities of the Mariscal Sucre International Airport in Quito Ecuador.}
    \item{I assessed if the animal presented any harm to itself, the public or any aircrafts by estimating their monthly and seasonal home  \\ ranges, and resource selection functions using the R programming language.\\ }
  \end{cvitems}
}
%---------------------------------------------------------
  \cventry
    {Thesis Evaluating Committee} % Job title
    {Universidad Distrital Francisco José de Caldas} % Organization
    {Bogotá, Colombia} % Location
    {2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Undergraduate Thesis: “Biological knowledge status of the subfamily Stenodermatinae (Gervais, 1856): a
        cytogenetic \\ revision within an evolutionary framework”.\\}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Field and Research Assistant} % Job title
    {Laboratorio de Genética Evolutiva, Universidad Nacional de Misiones} % Organization
    {Posadas, Argentina} % Location
    {Aug. 2014 -- Apr. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {I was part of collection campaigns with the goal of obtaining biological samples from bats for several genetic and \\ ecological projects.}
        \item{As an undergraduate student I was trained in cytogenetic and molecular methods to study the evolution.}
      \end{cvitems}
    }

    %---------------------------------------------------------
\end{cventries}
