%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Collaborator} % Job title
    {The Ray Lab (2021 - Present)} % Organization
    {Lubbock, USA} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Ecuadorian bats: A key to investigating aging and metabolic trade-offs based on feeding habits and transposable element
evolution}
        \item {Bat1K: An international effort to sequence and assemble the genomes of every extant bat species.}
        \item {RAPID: Immunological adaptations in bats to moderate the effect of
        coronavirus infection.}
        \item {RoL: FELS: EAGER: Collaborative Research: Genomics of exceptions to
        scaling of longevity to body size.}
      \end{cvitems}
    }

  \cventry
    {Associated Researcher} % Job title
    {Instituto Nacional de Biodiversidad (2020 - Present)} % Organization
    {Quito, Ecuador} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Employed novel bioinformatic methods to understand how
        mammals make use of their natural habitat and what \\ resources
        impact on how they move across their home ranges.}
        \item {Used multivariate analysis methods and machine learning to assess discrimination levels among rodent taxa.}
      \end{cvitems}
    }

  \cventry
    {Scientific Director} % Job title
    {Fundación Oso Andino (2020 - Present)} % Organization
    {Quito, Ecuador} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {As part of the Large Mammals Project in Parque Nacional Cayambe
        Coca, I assisted in ecotourism projects and tracking \\ of mammals.}
        \item {We work with INABIO on several projects related to
        home range estimation of mammals habitats and behavior \\ patterns
        using GPS data.}
        \item {We have teamed up with colombian institutions to study how Andean bears select their environments and assess \\ environmental diel preferences.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
